---
title: 'Twin Pandemics: Documenting the Increase in Domestic Violence During the COVID-19
  Pandemic'
output:html_notebook
---

**REPORTING QUESTIONS**

*Who are the populations most impacted by domestic violence in 2020?*

*How did the pandemic impact domestic violence?*

**LOADING TIDYVERSE AND IMPORTING DATA**

```{r}
#Load Tidyverse

library(tidyverse)

#Import LAPD crime data 2020

read_csv("Crime_Data_from_2020_to_Present.csv", 
         col_types = cols(`Date Rptd` = col_datetime(format = "%m/%d/%Y %H:%M:%S %p"), 
                          `DATE OCC` = col_datetime(format = "%m/%d/%Y %H:%M:%S %p"), 
                          `TIME OCC` = col_character(), `Part 1-2` = col_number(), 
                          `Crm Cd` = col_character(), `Vict Age` = col_character(), 
                          `Premis Cd` = col_number(), LAT = col_number(), 
                          LON = col_number()))
View(Crime_Data_from_2020_to_Present)
```

**FILTERING DATE DATA**

I am filtering using OCC Date data because it is the date the incident occured as opposed to the date the incident was reported to LAPD

```{r}
#Filtering Crimes for Year 2020

library(lubridate)
library(dplyr)

#format date field
Crime_Data_from_2020_to_Present$`DATE OCC` <- as.Date(Crime_Data_from_2020_to_Present$`DATE OCC`, format = "%m/%d/%Y %H:%M:%S %p")

crime_data_2020 <- Crime_Data_from_2020_to_Present %>%
  filter(Crime_Data_from_2020_to_Present$`DATE OCC` >= as.Date("2020-01-01") & Crime_Data_from_2020_to_Present$`DATE OCC` <= as.Date("2020-12-31"))

view(crime_data_2020)
```

**ISOLATING MOCODE 2000**

I am using MO CODE 2000 - Domestic violence to capture all crime incidents where domestic violence was a factor. Using USR codes leaves out crimes such as homicide and rape where domestic violence was a motive.

```{r}
#Filter MO CODE 2000 - Code for Domestic Violence

mo_code_2000 <- crime_data_2020 %>%
  filter(grepl('2000', crime_data_2020$Mocodes))

head(mo_code_2000)
```
